\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-26 manuscript/manuscript.tex
temperature

\subsection{Precipitation in Mansfield Connecticut}
\label{sec:precipitation}
Annual maximums of hourly precipitation in inches time series data were 
retrieved 
from the Chicago Midway International Airport (MDW), New York LaGuardia 
International 
Airport (LGA),
and Los Angeles International Airport (LAX) stations from the 
National Oceanic and Atmospheric Administration. These stations were selected 
from places of importance in the three largest American cities. LGA and
MDW were chosen over John F. Kennedy and O'Hare as more data was available
from these stations. The data for MDW is from
1948 to 2014, the data for LGA is from 1948 to 2013, and the
data for LAX is also from 1948 to 2013. We can apply our method (as well
as the non-parametric bootstrap KS Test \citep{babu2004goodness} and
the parametric bootstrap KS Test) to
the precipitation time series from each of these locations to test if they
follow the
Generalized Extreme Value (GEV) distribution using the \textsl{evd} 
package \citep{evd}. Precipitation maximum series 
typically do follow the GEV distribution, so we expect to fail to reject the
null hypothesis.

@@

>>>>

\subsection{Precipitation at Airports}
\label{sec:precipitation}
Annual maximums of hourly precipitation in inches time series data were 
retrieved 
from the Chicago Midway International Airport (MDW), New York LaGuardia 
International 
Airport (LGA),
and Los Angeles International Airport (LAX) stations from the 
National Oceanic and Atmospheric Administration (NOAA). These stations were selected 
from places of importance in the three largest American cities. LGA and
MDW were chosen over John F. Kennedy and O'Hare as more data was available
from these stations. The data for MDW is from
1948 to 2014, the data for LGA is from 1948 to 2013, and the
data for LAX is also from 1948 to 2013. We can apply our method (as well
as the non-parametric bootstrap KS Test \citep{babu2004goodness} and
the parametric bootstrap KS Test) to
the precipitation time series from each of these locations to test if they
follow the
Generalized Extreme Value (GEV) distribution using the \textsl{evd} 
package \citep{evd}. Precipitation maximum series 
typically do follow the GEV distribution, so we expect to fail to reject the
null hypothesis.

@@

\subsection{Temperature in Central Park}
\label{sec:temperature}

Annual temperature maximums recorded in Central Park, New York, NY from
1895 to 2023 were sourced from the NOAA. Again, we are interested in seeing
if our method, which
accounts for serial dependence and does not require parameter specification,
performs differently than the non-parametric bootstrap KS Test 
\citep{babu2004goodness} and the parametric bootstrap KS Test, neither of
which account for serial dependence. We found that when using our method,
the p-value for the test that the series follows the GEV distribution is 0.1420.
When using Babu's method, the p-value is 0.0666, and when using the parametric
method, the p-value is 0.0682. At the common significance level of .05,
the conclusions would be the same regardless of the method used. However, it
is clear that for this series, our method more decisively fails to reject the 
null hypothesis at a significance level of .10.
